The LHC as a Neutrino-Ion Collider

### 2023-12-05 journal_sub/app-hllhc.tex
working on paper revision

\section{Phenomenology of HL-LHC}
\label{app:comparisons_with_HLLHC}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!h]
	\centering
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\caption{Same as}
	\label{fig:HLLHC_pheno_integrated}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the following section, we repeat the same phenomenology studies as in
Sec.~\ref{sec:pheno} but using the High-Luminosity LHC (HL-LHC) PDF 
from~\cite{AbdulKhalek:2018rok}.
%
Such comparisons present a complementary study to the impact seen both at the PDF 
and prediction level shown in Sec.~\ref{sec:pheno}. The PDF constraints from the 
FPF and HL-LHC experiments are fully orthogonal in that the former have the very 
important property that possible contamination from new physics on the PDF fits 
can be completely ignored, since this process is driven by $Q^2$ values outside 
the possible presence of BSM physics.
%
Specially, should anomalies be revealed at the HL-LHC, having the fully independent
validation of the large-$x$ PDFs provided by the FPF would be extremely valuable 
for its interpretation.

In Fig.~\ref{fig:HLLHC_pheno_integrated} are displayed the fiducial cross-sections for 
representative LHC processes, similar to the ones shown in Fig.~\ref{fig:NNPDF40_pheno_integrated},
but evaluated with PDF4LHC15 and its variant that includes HL-LHC projections (``\_HLLHC'').
The corresponding differential cross-sections are shown in Fig.~\ref{fig:HLLHC_pheno_differential}.
%
Concerning the fiducial cross-sections, a significant reduction in PDF uncertainties
is seen, reaching up to a factor of four for processes involving single boson productions. 
Such a significant decrease in the PDF uncertainties is also observed at the differential
level.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[htbp]
	\centering
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-global-HLLHC.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-global-HLLHC.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-global-HLLHC.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-global-HLLHC.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-global-HLLHC.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-global-HLLHC.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-global-HLLHC.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-global-HLLHC.pdf}
	\includegraphics[width=0.49\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-global-HLLHC.pdf}
	\caption{Same as Fig.~\ref{fig:NNPDF40_pheno_integrated}
		for the corresponding differential distributions in the case of NNPDF4.0
		%
	}
	\label{fig:HLLHC_pheno_differential}
\end{figure*}

>>>>

\section{Comparison with HL-LHC PDF projections}
\label{app:comparisons_with_HLLHC}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[!h]
	\centering
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_DY_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WM_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WP_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HVBF_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWP_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_HWM_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPWM_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WPZ_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\includegraphics[width=0.32\textwidth]{plots/LHCpheno/NNPDF_WMZ_14TEV_40_PHENO-integrated-HLLHC.pdf}
	\caption{The same LHC fiducial cross-sections as in Fig.~\ref{fig:NNPDF40_pheno_integrated},
          now comparing the PDF4LHC15 baseline predictions with those based
          on the PDFs including HL-LHC pseudo-data from~\cite{AbdulKhalek:2018rok}.
          %
          Specifically, we consider the HL-LHC PDF projections
          from ``Scenario B'', corresponding to an intermediate scenario for the expected reduction
          of systematic uncertainties. }
	\label{fig:HLLHC_pheno_integrated}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Here we revisit the phenomenology studies as in
Sec.~\ref{sec:pheno} but using the High-Luminosity LHC (HL-LHC) PDF 
from~\cite{AbdulKhalek:2018rok}.
%
Such comparisons present a complementary study to the impact seen both at the PDF 
and prediction level shown in Sec.~\ref{sec:pheno}. The PDF constraints from the 
FPF and HL-LHC experiments are fully orthogonal in that the former have the very 
important property that possible contamination from new physics on the PDF fits 
can be completely ignored, since this process is driven by $Q^2$ values outside 
the possible presence of BSM physics.
%
Specially, should anomalies be revealed at the HL-LHC, having the fully independent
validation of the large-$x$ PDFs provided by the FPF would be extremely valuable 
for its interpretation.

In Fig.~\ref{fig:HLLHC_pheno_integrated} The same LHC fiducial cross-sections as in Fig.~\ref{fig:NNPDF40_pheno_integrated},
now comparing the PDF4LHC15 baseline predictions with those based
on the PDFs including HL-LHC pseudo-data from~\cite{AbdulKhalek:2018rok}.
%
Specifically, we consider the HL-LHC PDF projections
from ``Scenario B'', corresponding to an intermediate scenario for the expected reduction
of systematic uncertainties.
 %
Concerning the fiducial cross-sections, a significant reduction in PDF uncertainties
is seen, reaching up to a factor of four for processes involving single boson productions. 
Such a significant decrease in the PDF uncertainties is also observed at the differential
level.

### 2023-12-05 journal_sub/sec-results.tex
working on paper revision

By following the strategy outlined in Sect.~\ref{sec:dis_pseudodata}, we 
quantify the impact on the proton and nuclear PDFs of differential  DIS
cross-section measurements obtained with the  LHC neutrino beam. 
%
Here we present results first for the Hessian profiling of the PDF4LHC21,
then for the Monte Carlo fit NNPDF4.0, and finally for the nuclear PDFs of EPPS21, also
by means of profiling.
%
We study the stability of the results with respect to the inclusion of systematic uncertainties,
charm-tagged data, and lepton-charge separation.
%
We also compare the impact of the different FPF experiments separately and provide
results for their combination.
%
For completeness, we study the constraints on PDFs 
provided by the forward experiments, namely FASER$\nu$. The results show that measurements
at FASER$\nu$ are unable to further improve the determination of PDFs therefore strengthening the
need for the FPF experiments.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{
The fractional PDF uncertainties (at the 68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 structure
functions are included.
%
The FASER$\nu$2 impact projections are presented both without and with systematic
uncertainties accounted for, and include charm-tagged structure functions
as well as final-state lepton-charge separation.
%
}
\label{fig:FASERnu2_baseline}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\paragraph{Constraints from FASER$\nu$2.}
%
Fig.~\ref{fig:FASERnu2_baseline} shows the
fractional uncertainties (at the 68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$2 structure functions are
added by means of Hessian profiling.
%
The FASER$\nu$2 pseudo-data accounts for  both  inclusive and charm-tagged structure functions
and assumes outgoing lepton- charge identification.
%
We display results for the profiling in which the experimental covariance matrix
considers only statistical uncertainties, as well as for the scenario where
statistical and systematic errors are added in quadrature following
the procedure spelled out in Sect.~\ref{subsec:uncertainties}.
%
We restrict the comparisons to the region $10^{-3}\lsim x \lsim 0.7$ covered
by the LHC neutrino experiments (see also Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF}).
%
In addition of a reduction of PDF uncertainties, the Hessian profiling
also results in general in a shift in the PDF central values.
%
This shift is however arbitrary, since it 
depends on the fluctuations
entering the pseudo-data generation, and is hence ignored in the following.

Inspection of Fig.~\ref{fig:FASERnu2_baseline} reveals that measurements of DIS structure
functions at FASER$\nu$2 would reduce PDF uncertainties on the quark and antiquark
PDFs, while leaving
the gluon essentially unaffected.
%
As expected for a neutrino scattering experiment, its impact is most marked for
those PDF combinations sensitive to quark flavour separation such as
the up and down valence PDF as well as the total strangeness.
%
Indeed, the reduction of PDF uncertainties is particularly significant for the latter,
a consequence of the inclusion of charm-tagged structure functions in the fit.
%
Given that all PDF determinations entering PDF4LHC21 already include existing neutrino
DIS measurements, the fact that FASER$\nu$2 pseudo-data still manages to improve
uncertainties highlights the new information provided by the LHC neutrino experiments.

@@

\paragraph{Experiment dependence.}
%
Together with those for FASER$\nu$2, we have also produced PDF impact projections for
other proposed FPF experiments, specifically for AdvSND and FLArE.
%
In the latter case, we consider the 10 tonne variant FLArE10.
%
Fig.~\ref{fig:FASERnu2_FLAre10} compares the PDF sensitivity
of FASER$\nu$2, in the scenario where systematic uncertainties are neglected, with the corresponding
results for AdvSND and FLArE10 respectively.
%
As summarised by Table~\ref{tab:integrated_rates}, each of these experiments
has associated different expected numbers of DIS events, namely 510k, 56k, and 110k (670k)
inclusive muon-neutrino events for FASER$\nu$2, AdvSND and FLArE10~(100) respectively,
with 76k, 7k, and 15k (90k) in the charm-tagged case.

@@

Applying the same procedure to FASER$\nu$ and SND@LHC structure
functions leaves the baseline  results from PDF4LHC21 essentially
unaffected, as demonstrated in App.~\ref{app:fasernu_runIII_impact},
and showing that for the current generation of LHC neutrino detectors
it will be difficult to provide competitive constraints on the proton structure due
to the (relatively) low DIS event rates.

@@

\paragraph{Impact of FASER$\nu$ Run III measurements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[htbp]
	\centering
	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
	\caption{Same as  Fig.~\ref{fig:FASERnu2_baseline} (statistical uncertainties only), comparing
		the projected PDF impact of FASER$\nu$2 with that of FASER$\nu$, in the latter
		case assuming the Run III integrated
		luminosity of $\mathcal{L}=150$ fb$^{-1}$.
	}
	\label{fig:FASERnu2_vs_FASERnu}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

The same procedure applied to the FPF experiments in earlier
can also be used in the case of FASER$\nu$, for which pseudo-data is generated
for a Run III integrated
luminosity of $\mathcal{L}=150$ fb$^{-1}$.
%
As indicated by Table~\ref{tab:integrated_rates}, by the end of Run III, one expects
that FASER$\nu$ will have recorded around 600 and 1800 electron- and muon-neutrinos
respectively corresponding to deep-inelastic scattering events, of which around 100
and 300 respectively are associated to charm-tagged events.
%
These projected event rates can be compared with the expectations for FASER$\nu$2, which predict
an increase in statistics of more than two orders of magnitude.

Fig.~\ref{fig:FASERnu2_vs_FASERnu} presents a similar comparison as that of
Fig.~\ref{fig:FASERnu2_baseline} now between the projected PDF impact of FASER$\nu$2 and that of
FASER$\nu$.
%
One finds that neutrino DIS measurements at FASER$\nu$ are unable to improve
PDF uncertainties as compared to the baseline scenario encapsulated by PDF4LHC21.
%
The reason is two-fold: the smaller event rates as compared to FASER$\nu$2,
and the reduced coverage of the $(x,Q^2)$ phase space shown in Fig.~\ref{fig:fasernu2_muon}.
%
The differences in PDF sensitivity between FASER$\nu$ and FASER$\nu$2 in
Fig.~\ref{fig:FASERnu2_vs_FASERnu} illustrate
the  importance of realising the FPF in order to exploit the full physics potential enabled 
by LHC neutrinos for QCD and hadron structure studies.

>>>>

By following the strategy outlined in Sect.~\ref{sec:dis_pseudodata}, we 
quantify the impact on the proton and nuclear PDFs of differential  DIS
cross-section measurements obtained with the  LHC neutrino beam. 
%
Here we present results first for the Hessian profiling of the PDF4LHC21,
then for the Monte Carlo fit NNPDF4.0, and finally for the nuclear PDFs of EPPS21, also
by means of profiling.

First of all, we study the constraints on the PDFs 
provided by FASER$\nu$ during the LHC Run III data taking period,
showing that they are not able to improve the determination of PDFs.
%
We then move to study the impact of the FPF experiments, focusing
on FASER$\nu$2.
%
We study the stability of the results with respect to the inclusion of systematic uncertainties,
charm-tagged data, and lepton-charge separation.
%
We also compare the impact of the different FPF experiments separately and provide
results for their combination.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[htbp]
	\centering
	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_uv_ratio.pdf}
	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_dv_ratio.pdf}
	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_g_ratio.pdf}\\
	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_Sea_ratio.pdf}
	\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/FASERv2_vs_FASERv/statOnly_FASERv_q2_10000_pdf_s_ratio.pdf}
	\caption{
The fractional PDF uncertainties (at the 68\% CL) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
in the PDF4LHC21 baseline, compared to the results obtained once the FASER$\nu$
and FASER$\nu$2 structure functions are included in the fit.
%
In both cases we include charm-tagged structure functions
and assume final-state lepton-charge separation.
%
The FASER$\nu$ projections are based on a Run III integrated
luminosity of $\mathcal{L}=150$ fb$^{-1}$.
	}
	\label{fig:FASERnu2_vs_FASERnu}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\paragraph{Impact of the FASER$\nu$ Run III measurements.}
%
Fig.~\ref{fig:FASERnu2_vs_FASERnu} shows the
fractional uncertainties (at the 68\% confidence level) at $Q^2 = 10^4 \, \textrm{GeV}^2$ 
for the up and down valence quarks, gluon, total quark singlet, and total strangeness PDFs
in the PDF4LHC21 baseline, compared to the results obtained once the  FASER$\nu$
and FASER$\nu$2 structure functions are
added by means of Hessian profiling.
%
In both cases we include charm-tagged structure functions
and assume final-state lepton-charge separation.
%
The FASER$\nu$ projections are based on a Run III integrated
luminosity of $\mathcal{L}=150$ fb$^{-1}$.
%
As indicated by Table~\ref{tab:integrated_rates}, by the end of Run III, one expects
that FASER$\nu$ will have recorded around 600 and 1800 electron- and muon-neutrinos
respectively corresponding to deep-inelastic scattering events, of which around 100
and 300 respectively are associated to charm-tagged events.
%
We display results for the profiling in which the experimental covariance matrix
considers only statistical uncertainties.
%
We restrict the comparisons to the region $10^{-3}\lsim x \lsim 0.7$ covered
by the LHC neutrino experiments (see also Fig.~\ref{fig:Kin_nNNPDF30_EIC_FPF}).

From Fig.~\ref{fig:FASERnu2_vs_FASERnu}
we find that neutrino DIS measurements at FASER$\nu$ are unable to improve
PDF uncertainties as compared to the baseline scenario encapsulated by PDF4LHC21.
%
The reason is two-fold: the smaller event rates as compared to FASER$\nu$2,
and the reduced coverage of the $(x,Q^2)$ phase space shown in Fig.~\ref{fig:fasernu2_muon}.
%
The differences in PDF sensitivity between FASER$\nu$ and FASER$\nu$2 in
Fig.~\ref{fig:FASERnu2_vs_FASERnu} illustrate
the  importance of realising the FPF in order to exploit the full physics potential enabled 
by LHC neutrinos for QCD and hadron structure studies.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}[t]
\centering
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_uv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_dv_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_g_ratio.pdf}\\
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_Sea_ratio.pdf}
\includegraphics[width=0.32\textwidth]{plots/proton_fasernu2/inclusive+charm_chargediscrimination/fred05fcorr05_FASERv2_q2_10000_pdf_s_ratio.pdf}
\caption{Same as in Fig.~\ref{fig:FASERnu2_vs_FASERnu} comparing
  the FASER$\nu$2 impact projections without and with systematic
uncertainties accounted for in the experimental covariance matrix.
}
\label{fig:FASERnu2_baseline}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Constraints from FASER$\nu$2.}
%
Fig.~\ref{fig:FASERnu2_baseline} shows the
same comparison as in as in Fig.~\ref{fig:FASERnu2_vs_FASERnu}, now for the
  the FASER$\nu$2 impact projections without and with systematic
  uncertainties accounted for in the experimental covariance matrix,
  following
the procedure spelled out in Sect.~\ref{subsec:uncertainties}.
%
The FASER$\nu$2 pseudo-data accounts for  both  inclusive and charm-tagged structure functions
and assumes outgoing lepton- charge identification.
%
We display results for the profiling in which the experimental covariance matrix
considers only statistical uncertainties, as well as for the scenario where
statistical and systematic errors are added in quadrature.
%
In addition of a reduction of PDF uncertainties, the Hessian profiling
also results in general in a shift in the PDF central values.
%
This shift is however arbitrary, since it 
depends on the fluctuations
entering the pseudo-data generation, and is hence ignored in the following.

Inspection of Fig.~\ref{fig:FASERnu2_baseline} reveals that, as opposed
to the FASER$\nu$ impact projections, measurements of DIS structure
functions at FASER$\nu$2 would reduce PDF uncertainties on the quark and antiquark
PDFs, while leaving
the gluon essentially unaffected.
%
As expected for a neutrino scattering experiment, its impact is most marked for
those PDF combinations sensitive to quark flavour separation such as
the up and down valence PDF as well as the total strangeness.
%
Indeed, the reduction of PDF uncertainties is particularly significant for the latter,
a consequence of the inclusion of charm-tagged structure functions in the fit.
%
Given that all PDF determinations entering PDF4LHC21 already include existing neutrino
DIS measurements, the fact that FASER$\nu$2 pseudo-data still manages to improve
uncertainties highlights the new information provided by the LHC neutrino experiments.

@@

\paragraph{Experiment dependence.}
%
Together with the impact projections for FASER$\nu$2, we have also produced analogous results for
other proposed FPF experiments, specifically for AdvSND and FLArE.
%
In the latter case, we consider the 10 tonne variant, FLArE10.
%
Fig.~\ref{fig:FASERnu2_FLAre10} compares the PDF sensitivity
of FASER$\nu$2, in the scenario where systematic uncertainties are neglected, with the corresponding
results for AdvSND and FLArE10 respectively.
%
As summarised by Table~\ref{tab:integrated_rates}, each of these experiments
has associated different expected numbers of DIS events, namely 510k, 56k, and 110k (670k)
inclusive muon-neutrino events for FASER$\nu$2, AdvSND and FLArE10~(100) respectively,
with 76k, 7k, and 15k (90k) in the charm-tagged case.

@@

@@
